---
title: "Investigating the factors that are related to medical costs in the United States"
author: "Jianhong Dong, Xueyao Wang"
date: "`10.28.2022`"
output:
  pdf_document:
         latex_engine: xelatex
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MASS)
library(lmtest)
library(car)
library(olsrr)
library(plyr)
library(rcompanion)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(ggmosaic)
library(gridExtra)
options(tinytex.verbose = TRUE)
```

Group member contributions: \
Xueyao Wang (library research & coding) 60% \
Jianhong Dong (background & typesetting) 40% \

```{r summary}
ins <- read.csv("/Users/sherrywang/Desktop/UW/Stat 302/insurance.csv")
```

## Section 1: Introduction

### Background  

<br>
Health cost in America has been increasing every year and this year in 2022, the US health insurance prices went up 28.2% since September due to the pandemic. 

### Dataset  
<br>
This is the dataset we chose: \


### Reason to chose  
<br>
We selected this dataset due to our interest in public health and the health situations faced by families. With healthcare costs rising significantly each year, we aim to understand which health variables, like those in this dataset, might influence medical expenses. Additionally, we seek to explore any potential relationships between these health variables. 

### Population and sample
<br>
Population: all health insurance contractors in the US. \
Sample: 1338 insurance contractors selected. \

### Type of study
<br>
This is a cross-sectional study. \

### Software and version
<br>
R studio, version: 2022.02.3 \

### Level of significance
<br>
$\alpha$ = 0.05 \

###  Missing values
<br>
We intend to filter out the missing values. \

### Significance of study
<br>
Accurately predicting insurance costs based on data is crucial for insurance companies, as profitability depends on spending less than what is collected. This analysis is essential, as it can help identify which variables significantly predict insurance costs (Uzila, 2022). \


### Research Questions
<br>

#### Q1 Is there an association between the gender(sex) and the smoking status (smoker) of an insurance contractor, controlling the regions? 
 \
 \
Methods and plans: We will begin by using the Cochran-Mantel-Haenszel (CMH) test to determine whether region influences the relationship between gender and smoking status. If no significant influence is found, we will exclude region as a variable. If region is found to have a significant effect, we will proceed by performing a chi-square test within each region to assess the relationship between gender and smoking status. \

Variables: Our dependent variable is smoking status, while our independent variable is sex. We will also assess whether region acts as a confounding variable. \

Why interested: We aim to determine whether the probability of smoking differs between genders and to assess if region plays a role in this difference. \

#### Q2 Is there an association between the region and the medical cost of insurance contractor (charges)? 
 \
 \
Methods and plans: We will first test the assumptions for ANOVA. If these assumptions are met, we will perform ANOVA to examine whether there is a difference in mean medical costs across regions. If the assumptions are not fulfilled, we will use the non-parametric Kruskal-Wallis test to assess the difference in means. Additionally, we will identify and remove any outliers and compare results before and after their removal. If a significant difference in means is found between regions, a post hoc test will be conducted to determine specific differences between regions. \

Variables: We will use region as our independent variable and charges as our dependent variable. \

Why interested: Given that regions differ in factors such as cost of living and tax rates, we are interested in finding out if medical costs also vary by region. \

#### Q3 Which factors significantly predict the total medical cost of insurance contractors(charges)? 
 \
 \
Methods and plans: We will start by applying multiple linear regression using all variables. Next, we will reduce unnecessary variables through backward selection, previous results, and relevant literature to identify the best model. \

Variables: Charges is our dependent variable, and we will include all other variables (sex, smoker, region, children, age, bmi) in our full model. We will also create a second model excluding the variable sex and a third model excluding both sex and region. \

Why interested: We are interested in identifying which variables significantly impact insurance medical costs so that people can understand which factors are most predictive of charges. \

## Section 2 Exploratory and descriptive data analysis

### Variable Overview

#### 3 categorical variables: 
\
\
Sex: insurance contractor gender (female, male). \
Smoker : smoking (yes or no). \
Region: the beneficiary's residential area in the US(northeast, southeast, southwest, northwest). \
  
#### 4 numerical variables: 
\
\
Age: age of primary beneficiary \
Bmi: body mass index, providing an understanding of body, weight in kilograms divided by height in meters squared. \
Children: number of children covered by health insurance / Number of dependents. \
Charges: individual medical costs billed by health insurance. \

```{r Variables}
data.frame(
  Variables = c("age", "sex", "bmi", "children", "smoker", "region", "charges"),
  DataType = c("Numerical", "Categorical", "Numerical", "Numerical", 
               "Categorical", "Categorical", "Numerical"),
  MeasurementLevel = c("Ratio", "Nominal", "Ratio", "Ratio", "Nominal",
                       "Nominal", "Ratio"),
  Units = c("Years", "NA", "kg/m^2", "NA", "NA", "NA", "Dollars"), 
  stringsAsFactors = FALSE
)
summary(ins)

```

### Variables for Q1: smoker, sex and region 

```{r Q1Var}
# Individual ggplot2 plots
Q1_1 <- ggplot(ins, aes(x = smoker)) + 
  geom_bar() + 
  labs(title = "Smoking status", x = "Smoker", y = "Count") + 
  theme_bw(base_size = 16) + 
  theme(plot.title = element_text(hjust = 0.5))

Q1_2 <- ggplot(ins, aes(x = sex)) + 
  geom_bar() + 
  labs(title = "Sex", x = "Sex", y = "Count") + 
  theme_bw(base_size = 16) + 
  theme(plot.title = element_text(hjust = 0.5))

Q1_3 <- ggplot(ins, aes(x = region)) + 
  geom_bar() + 
  labs(title = "Regions in US", x = "Region", y = "Count") + 
  theme_bw(base_size = 16) + 
  theme(plot.title = element_text(hjust = 0.5))

Q1_4 <- ggplot(data = ins) +
  geom_mosaic(aes(x = product(smoker, region, sex), fill = smoker)) +
  labs(x = "Smoker:Sex", y = "Region", 
       title = "Number of smokers of both sexes \
       controlling for regions") +
  theme(plot.title = element_text(hjust = 0.5))

# Arrange plots in a 2x2 grid
grid.arrange(Q1_1, Q1_2, Q1_3, Q1_4, ncol = 2)

```

From the left graphs and top right graph above, we can see that the number of non-smoking people is much higher than the smokers.  The data is collected from both genders equally. Finally, the dataset contains more people from southeast region in the US.

From the mosaic plot, the x-axis represents the smoking status with sex, and the y-axis represents different regions. The pink bar shows the portion of people who are not smokers and the blue bar represents the portion of people who are smokers. We can first see that the number of people who are not smoker is the majority for every region and both genders. Then, the number of female smoker is obviously fewer than male in every region. Comparing the smoking status among regions, we can tell that the number of people who are not smokers is approximately the same within each gender, whle the number of people who are smokers is the highest in southeast region for both genders.

We then made the contingency table for sex and smoking status to demonstrate the frequency for each sex to smoke.

```{r Q1Table}
SmokeSexRegion <- table(ins$smoker, ins$sex, ins$region)
dimnames(SmokeSexRegion) <- list(Smoke = c("No","Yes"), 
                                  Sex = c("Female","Male"), 
                                  Region = c("Northeast", "Northwest", 
                                             "Southeast", "Southwest"))
SmokeSexRegion
```

### Variables for Q2: charges and region

The region is already shown in former bar graph, so we visualized the charges.

```{r Q2Var}
Q2_1 <- ggplot(ins, aes(y = charges)) + 
  labs(title = "Medical cost (charges) of \
  insurance contractor",
       y = "") +
  geom_boxplot() +
  theme(plot.title = element_text(size = 12), 
        axis.title.x = element_text(size = 10), 
        axis.title.y = element_text(size = 10)) 

Q2_2 <- ggplot(ins, aes(x = region, y = charges)) + 
  geom_bar(stat = "identity") + 
  labs(title = "Medical cost (charges)\
  in different region of US",
       x = "Region",
       y = "Charges (dollars)") + 
  theme_bw(base_size = 16) + 
  theme(plot.title = element_text(size = 12, hjust = 0.5), 
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10))

Q2_3 <- ggplot(ins, aes(x = region, y = charges)) + 
  labs(title = "Medical costs in different region of US",
       x = "Region",
       y = "Medical costs (dollars)") +
  geom_boxplot() +
  theme(plot.title = element_text(size = 12), 
        axis.title.x = element_text(size = 10), 
        axis.title.y = element_text(size = 10))

# Arrange plots in a 2x2 grid
grid.arrange(Q2_1, Q2_2, Q2_3, ncol = 2)
```

From the top left boxplot we can see that the charges are not normal as our dependent variable. Also, there are several extreme outliers.\

By visualizing the charges within each region shown in bar chart on the top right, we can see that the medical costs is southeast region is the highest among all the regions. Then, the medical costs in northeast region is a little higher than northwest and southwest regions.\

The bottom left shows that the quartiles for every regions are approximately the same, except for the higher Q3 for southeast region. In addition to that, we can see that there are some significant outliers in the regions.\

### Variables for Q3: age, bmi, children, smoker and charges

Since the Research Question 3 is to determine the factors that affect charges, we visualized the variables in our final model. Since smoker and charges have already been visualized in the former section, we omitted them.

```{r Q3Var}
Q3_1 <- ggplot(ins, 
       aes(y = age)) + 
  labs(title = "Age (years)",
       y = "",) +
  geom_boxplot()

Q3_2 <- ggplot(ins, 
       aes(y = bmi)) + 
  labs(title = "BMI",
       y = "",) +
  geom_boxplot()

Q3_3 <- ggplot(ins, 
       aes(y = children)) + 
  labs(title = "Number of children",
       y = "",) +
  geom_boxplot()

# Arrange plots in a 2x2 grid
grid.arrange(Q3_1, Q3_2, Q3_3, ncol = 2)
```

From the graphs above, we can see that for BMI, there are some extreme outliers. No significant outliers are found for age and children.

## Section 3 Statistical Results

### Research Question 1: Is there an association between the gender(sex) o and the smoking status (smoker) of an insurance contractor, controlling for the regions?

Independent variables: sex, region \
Dependent variable: smoker \

#### CMH test 
\
\
We first utilized CMH test to compare the odds ratio of sex and smoker for each regions. This is to determine whether the association of sex and smoker is different in each region. If so, region is a factor that influences the association of sex and smoker.

H0: the true common odds ratio of smoking status (smoker) between both genders (sex) among all regions in the US is equal to 1. \
H_a: the true common odds ratio of smoking status (smoker) between both genders (sex) among all regions in the US is not equal to 1. \

```{r Q1CMH}
mantelhaen.test(ins$sex, ins$smoker,ins$region)
```

As the p-value is 0.007447 < 0.05, there is sufficient evidence for us to reject the null hypothesis and conclude that the true common odds ratio of smoking status (smoker) between both genders (sex) among all regions in the US is not equal to 1, meaning that there is a difference in odds for the gender (sex) o and the smoking status (smoker) in different regions.

#### Chi-square test 
\
\
Now we need to determine the significance of sex and smoker association within each region using chi-square.

We checked the assumptions of chi-square: \
  1. Both variables are categorical. \
  2. All observations are made independently. \
  3. Cells in the contingency table are mutually exclusive. \
  4. Expected value of cells should be 5 or greater in at least 80% of cells. \

$H_0:$ there is no significanrt correlation between sex and smoker in the corresponding region. \
$H_A:$ there is significanrt correlation between sex and smoker in the corresponding region. \

```{r Q1Chi}
Northeast <- filter(ins, ins$region == "northeast")
chisq.test(Northeast$sex, Northeast$smoker)
Northwest <- filter(ins, ins$region == "northwest")
chisq.test(Northwest$sex, Northwest$smoker)
Southeast <- filter(ins, ins$region == "southeast")
chisq.test(Southeast$sex, Southeast$smoker)
Southwest <- filter(ins, ins$region == "southwest")
chisq.test(Southwest$sex, Southwest$smoker)
```

From the result above, we can see that at 5% significance level, only data in southwest region provides sufficient evidence for us to reject the null hypothesis and conclude that there is a significant association between sex and smoker. The result in southeast region shows a significant association between sex and smoker at 10% significance level, but not at 5% significant level.

### Research Question 2: Is there an association between the region and the medical cost of insurance contractor (charges)?

Independent variable: region \
Dependent variable: charges \

First, we need to compare the mean medical costs in each region. We need to test the ANOVA assumption to see if it is appropriate to use.

#### Anova 
\
\
Assumptions: \
1. The one way ANOVA has one single dependent variable (charges) and a single independent variable (region) \
2. Dependent variable(charges) is continuous, independent variable(region) is categorical and they are independent of each other \  
3. Each insurance contractor provided only one score for charges \
4. The normality assumption is not fulfilled \

```{r Q2ChargesNorm}
shapiro.test(ins$charges)
```

The dependent variable (charges) is not normally distributed. We tried several transformations to see if it can be transformed into normal data.

```{r Q2Transform}
shapiro.test(sqrt(ins$charges))
shapiro.test(ins$charges^2)
shapiro.test(log(ins$charges))
bc <- boxcox(ins$charges ~ ins$region)
lambda <- bc$x[which.max((bc$y))]
lambda
shapiro.test((ins$charges^lambda-1)/lambda)
```

After transformation, the data is still not normally distributed. So the normality assumption is not fulfilled.

5. The equal variance assumption is not fulfilled

```{r}
leveneTest(ins$charges ~ as.factor(ins$region))
```
Since p = 0.00086 < $\alpha$ = 0.05, the two groups do not have equal variance.

6. From the boxplot visualized in Section 2, there are some significant outliers for each region. \

Since the dependent variable is not normally distributed, the groups do not have equal variance and there are outliers. Thus, the ANOVA assumptions are not fulfilled and we will use the non-parametric Kruskal-Walllis test instead.\

#### Kruskal-Wallis test 
\
\
$H_0:$ there is no statistically significant difference in mean medical cost of insurance contractor (charges) among different regions (region). \
$H_A:$ there is statistically significant difference in mean medical cost of insurance contractor (charges) among different regions (region). \

```{r}
kruskal.test(ins$charges ~ ins$region)
```

Since p-value = 0.1923 > $\alpha$ = 0.05, we failed to reject the null hypothesis and conclude that there is no statistically significant difference in mean medical cost of insurance contractor (charges) among different regions. So there is no association between the region and the medical cost of insurance contractor (charges). 

#### Outliers removal 
\
\
As there is a lot of outliers, we tried to get rid of the outliers and do the kruskal test again to see the change in result.

```{r Q2MeanSD}
mean(ins$charges)
sd(ins$charges)
```

Since we know that the mean of charges is 13270.42, and the standard deviation of charges is 12110.01, so we can calculate z-scores to get rid of any extreme outlier that is 3 standard deviation away from mean using this formula: 

$$Z = \frac{x - \mu} {\sigma}$$

```{r Q2Outlier}
chargeFilter <- ins %>% 
  select(region, charges) %>%
  filter((charges - 13270.42)/12110.01 > -3 & (charges - 13270.42)/12110.01 < 3)

ggplot(chargeFilter, 
       aes(x = region, y = charges)) + 
  labs(title = "Medical costs in different region of US without outliers",
       x = "Region",
       y = "Medical costs (dollars)") +
  geom_boxplot()
```

We have already get rid of the extreme outliers according to the boxplot. Then we checked the ANOVA assumptions that was not fulfilled.

Normality:

```{r Q2NewNorm}
shapiro.test(chargeFilter$charge)
```

Since p-value < 2.2e-16 and it is far less than $\alpha$ = 0.05, the charges is still not normal.

Equal variance:

```{r Q2NewVar}
leveneTest(chargeFilter$charge ~ as.factor(chargeFilter$region))
```

Since the p-value = 0.0005383 < $\alpha$ = 0.05, the assumption of equal variance is still not fulfilled.

So we performed Kruskal-Wallis test again:

```{r}
kruskal.test(chargeFilter$charges ~ chargeFilter$region)
```

The p-value after outlier removal is 0.1633, which is reduced slightly from the p-value of the raw data (p-value = 0.1923). Since the p-value = 0.1633 > $\alpha$ = 0.05, we failed to reject the null hypothesis and conclude that there is no statistically significant difference in mean medical cost of insurance contractor (charges) among different regions after removal of outliers So there is still no association between the region and the medical cost of insurance contractor (charges).

### Research Question 3: Which factors significantly predict the total medical cost of insurance contractors(charges)?
  
Dependent variable: charges.

#### Multiple linear regression initial assumptions 
\
\
We checked the assumptions first:\

1. The dependent variable is not normal according to the previous test. Since all transformations did not work, we assume charges is normally distributed.\
2. multicollinearity \

For numerical variables:\
```{r}
cor(ins[, c(1,3,4)])
```

We can see the correlations between our numerical variables age, bmi and children are all weak (all of them are lower than 0.3).\

<br>
For categorical variables:\
sex vs smoker:\
```{r}
chisq.test(ins$sex, ins$smoker)
```

sex vs region:\
```{r}
chisq.test(ins$sex, ins$region)
```

smoker vs region:\
```{r}
chisq.test(ins$smoker, ins$region)
```

From above, we can see the categorical variables smoker and sex do have a statistically significant relationship in the 5% level of significance (0.006548 < $\alpha$= 0.05, so we can reject null).\

Hence, we may just keep one of variables(smoker and sex) in our following models to predict charges.\

#### Models comparison
\
\
We firstly kept all variables in the model.

Model 1 (full model): \
```{r Q3Mod1}
charges <- ins$charges
age <- ins$age
bmi <- ins$bmi
children <- ins$children
region <- ins$region
smoker <- ins$smoker
sex <- ins$sex

model1 <- lm(charges ~ age + bmi + children + as.factor(region) 
             + as.factor(smoker) + as.factor(sex)) # Full model
summary(model1)
```


$$Estimated charges = -11938.5 + 256.9 \cdot age + 339.2 \cdot bmi + 475.5 \cdot children - 353.0 \cdot regionnorthwest - 1034.36 \cdot regionsoutheast - 960.0 \cdot regionsouthwest + 23848.5 \cdot smokeryes - 131.3 \cdot sexmale$$
Then we performed backward selection to eliminate the variables that are unecessary. 

```{r Q3Back}
ols_step_backward_p(model1)
```

According to the result of backward selection, sex is an unecessary variable in our model. Moreover, according to the literature (Worrall et al., 1987), there are many confounding variables that may make the difference of medical cost between different genders(sex). Therefore, we removed sex in our model2.

Model 2:
```{r Q3Mod2}
model2 <- lm(charges ~ age + bmi + children + as.factor(region) 
             + as.factor(smoker)) # Model without sex
summary(model2)
```


$$EstimatedCharges = -11990.27  + 256.97 \cdot age + 338.66 \cdot bmi + 474.57 \cdot children - 352.18 \cdot regionnorthwest - 1035.0 \cdot regionsoutheast - 959.37 \cdot regionsouthwest + 23836.30 \cdot smokeryes$$

In Research Question 2, we have proved that there is difference in mean charges for each region. We also noticed that the p-value of chi-square between variable smoker and region is 0.06172, which is very close to our critical value 0.05.\

From the literature we found that the region difference may not play a very big role in predicting the health insurance coverage, which in turn would not influence the total medical cost of insurance contractors(charges) that much (Frenzen, 1993).\

Hence, we chose to remove region in model 3.

```{r Q3Mod3}
model3 <- lm(charges ~ age + bmi + children + as.factor(smoker) ) 
# Model without sex and region
summary(model3)
```

Model3:

$$EstimatedCharges = -12102.77  + 257.85  \cdot age + 321.85  \cdot bmi + 473.50  \cdot children + 23811.40  \cdot smokeryes$$

Then we compare the models.

```{r}
compareLM(model1, model2, model3)
```

We chose model 3 because the BIC for model 3 is the lowest (27150). The reason why we use BIC is because AIC prefers more complex models and it might choose models with a series of meaningless variables. So in reality, AIC is not a good choice for comparing models (Symonds et al., 2010). BIC, in contrast, employs prior knowledge and give simpler model.

Also, AIC is more suitable to use when there is a smaller sample size, while BIC is better if there is a large sample. As we have a large dataset, we choose to use BIC (Acquah et al., 2010).

#### Final model 
\
\
$$EstimatedCharges = -12102.77  + 257.85  \cdot age + 321.85  \cdot bmi + 473.50  \cdot children + 23811.40  \cdot smokeryes$$
Intercept: \
If a person has the age = 0, bmi = 0, number of children = 0 and the person is not a smoker, the estimated charges is -12102.77 dollars. \ 

Slopes: \
If a person has other variables remain, the increase in each year of age will increase the estimated charges by 257.85 dollars.\ 
If a person has other variables remain, the increase in each unit of bmi will increase the estimated charges by 321.85 dollars. \
If a person has other variables remain, the addition of each children in their family will increase the estimated charges by 473.50 dollars. \
If a person has other variables remain, the switching from non-smoker to smoker will increase the estimated charges by 23811.40 dollars. \

#### Prediction 
\
\
```{r Prediction}
person2 <- data.frame(age = 18,	sex = "male",	bmi = 33.770, children = 1, 
                      smoker = "no", region =	"southeast") 
#	Real charges = 1725.552 dollars
person2
predict(model3, person2)
```

We can see from the prediction that the result (3880.946 dollars) is much greater than the actual charge (1725.552 dollars). So there is an overestimate for the real charges.

#### Residual analysis 
\
\
```{r Residual}
par(mfrow = c(2,2))
plot(model3)
```

Linearity:\
```{r ResiLin}
raintest(model3)
```

The p-value is 0.07039 > $\alpha$ = 0.05, so we failed to reject the null hypothesis that the model is not linear. The linearity assumption is fulfilled.

Normality: \
```{r ResiNor}
resi <- model3$residuals
shapiro.test(resi)
```
The p-value is 2.2e-16 < $\alpha$ = 0.05, so there is sufficient evidence to conclude that the residue is not normal. The normality assumption is not fulfilled.

Homoskedasticity: \
```{r ResiHomo}
ols_test_breusch_pagan(model3)
```

The p-value is 4.494417e-52 < $\alpha$ = 0.05, so there is sufficient evidence to reject the null hypothesis that the vairances is equal. The Homoskedasticity assumption is not fulfilled.

Outlier: \
```{r ResiOut}
ols_plot_resid_stud(model3)
```

From the graph above there is no significant outlier.

Autocorrelation: \
```{r ResiAuto}
dwtest(model3)
```

Since p-value = 0.945 > 0.05, there is no auto-correlation

Multicolinearity: \
```{r ResiMul}
vif(model3)
```

Since the results are all below 5, so there is no significant multicolinearity.

## Section 4: Conclusion and Disscussion

#### Conclusion: 
\
\
First Research Question: We concluded that there is a difference in odds for gender (sex) and smoking status (smoker) across regions, indicating that region may act as a confounding variable. After conducting chi-square tests for each region, we found an association between gender and smoking status among insurance contractors in the Southwest but no association in the Northeast, Northwest, or Southeast. Literature suggests that smoking is a significant risk factor for coronary heart disease in both men and women, but smoking status may vary between genders (Bolego et al., 2002). \

Second Research Question: We found no association between region and medical costs (charges) for insurance contractors. This suggests that medical costs cannot be predicted based on the region where an insurance contractor resides. However, literature has suggested that medical costs may indeed vary by region (Uzila, 2021). \

Third Research Question: We concluded that age, BMI, number of children, and smoking status are significant predictors of medical costs (charges) for insurance contractors. These findings do not fully align with predictors released by federal healthcare authorities, which identified age, location, and individual or family enrollment (children) as the main predictors. Region was excluded in our model based on the conclusion from the second question ("How health insurance..."). \

#### Limitation:
\
\
We believe there are additional variables that could significantly impact the dependent variable, charges. For example, race may play an influential role. Additionally, there may be underlying reasons for the significance of certain variables in this dataset; for instance, rather than the number of children itself being significant, the true influence might stem from genetic diseases that run in families. \

This study focused exclusively on the medical costs of insured individuals, yet many people do not have health insurance. \

We also think the categorical variable region lacks specificity. There can be substantial differences within the same region; for example, NYC and a small city in Michigan are both in the same region, yet their medical costs likely vary widely. Thus, regions as defined here may not be fully representative. \


#### Suggestion:
\
\
Researchers could add race as a variable to examine any association with charges and include a categorical variable indicating whether the family has a history of genetic disease (yes or no). \

Instead of broad regions like Northeast, Northwest, Southeast, and Southwest, it might be more effective to specify location by state, providing greater specificity and potentially more accurate insights. \

## Section 5: Reference

1.\
Uzila, Albers (2021). Medical Cost Prediction Can we accurately predict medical costs based on people’s data?, Medium. 
https://towardsdatascience.com/medical-cost-prediction-4876e3449adf

<br>
2.\
Worrall, J. D., Appel, D., & Butler, R. J. (1987). Sex, marital status, and medical utilization by injured workers. Journal of Risk and Insurance, 27-44.
https://www.jstor.org/stable/252880#metadata_info_tab_contents

<br>
3.\
Frenzen, P. D. (1993). Health insurance coverage in US urban and rural areas. The Journal of Rural Health, 9(3), 204-214.
https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1748-0361.1993.tb00514.x

<br>
4.\
Symonds, M. R., & Moussalli, A. (2010). A brief guide to model selection, multimodel inference and model averaging in behavioural ecology using Akaike’s information criterion. Behavioral Ecology and Sociobiology, 65(1), 13-21. https://doi.org/10.1007/s00265-010-1037-6

<br>
5.\
Acquah, H. D. G. (2010). Comparison of Akaike information criterion (AIC) and Bayesian information criterion (BIC) in selection of an asymmetric price relationship. 
https://academicjournals.org/article/article1379662949_Acquah.pdf

<br>
6.\
Bolego, C., Poli, A., & Paoletti, R. (2002). Smoking and gender.Cardiovascular research,53(3), 568-576.
https://academic.oup.com/cardiovascres/article/53/3/568/325628

<br>
7.\
Finkelstein, E. A., Trogdon, J. G., Brown, D. S., Allaire, B. T., Dellea, P. S., & Kamal‐Bahl, S. J. (2008). The lifetime medical cost burden of overweight and obesity: implications for obesity prevention. Obesity,16(8), 1843-1848.
https://onlinelibrary.wiley.com/doi/full/10.1038/oby.2008.290

<br>
8.\
How health insurance marketplace® plans set your premiums. (n.d.). Get 2023 health coverage. Health Insurance Marketplace | HealthCare.gov. https://www.healthcare.gov/how-plans-set-your-premiums/

<br>
9.\
Uzila, A. (2022, January 27). Medical cost prediction. Medium. https://towardsdatascience.com/medical-cost-prediction-4876e3449adf
